|

### 2023-09-20 paper.Rmd
remove two lineup plots
remove frivolous mentions of packages and replace tidyverse package with tidyverse paper

@@

@@

These `R` packages are used for the work: 
`cli` [@cli], `curl` [@curl], `dplyr` [@dplyr], `ggplot2` [@ggplot2], `jsonlite` [@jsonlite], `lmtest` [@lmtest], `mpoly` [@mpoly], `progress` [@progress], `tibble` [@tibble], `ggmosaic` [@ggmosaic], `purrr` [@purrr], `tidyr` [@tidyr], `readr` [@readr], `stringr` [@stringr], `here` [@here], `kableExtra` [@kableextra], `patchwork` [@patchwork], `rcartocolor` [@rcartocolor]. The study website is powered by `PythonAnywhere` [@pythonanywhere] and the `Flask` web framework [@flask]. The `jsPsych` framework [@jspsych] is used to create behavioural experiments that run in our study website.

>>>>

<!----

@@

<!---

@@

These `R` packages are used for the work: `tidyverse` [@tidyverse], `lmtest` [@lmtest], `mpoly` [@mpoly], `ggmosaic` [@ggmosaic], `kableExtra` [@kableextra], `patchwork` [@patchwork], `rcartocolor` [@rcartocolor]. The study website is powered by `PythonAnywhere` [@pythonanywhere] and the `Flask` web framework [@flask]. The `jsPsych` framework [@jspsych] is used to create behavioural experiments that run in our study website.
